Latent Group Dropout for Multilingual and Multidomain Machine Translation

### 2022-04-13 2022/acl/acl_latex.tex
Added Ethical statement

@@

\section*{Ethic Statement}

>>>>

\section{Ethical Considerations}
MT technologies are generally intended to facilitate cross-lingual as well as cross-cultural communications. The methods presented here are notably interesting in the view to improve MT from and into English for low-resource languages, subject to the availability of data for a related language. We acknowledge that (a) our results should ultimately be backep-up large scale experiments involving much more languages -- even though this goes against the idea of limitating the computing cost our experiments; (b) better architectures and training regimes can improve the translation quality for low-resource languages, yet will not solve the problem entirely. This means that additional work focusing speciifically on developing resources for these languages should remain an important objective for future work.

@@
